Gametic Selection, Sex Ratio Bias, and Transitions Between Sex Determination Systems

### 2016-12-21 LaTeX/Turnover.tex
code for chromosome position plot done

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%W invasion versus position of selected locus
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgans}
\caption{
Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system regardless of how tightly it and the ancestral sex-determining locus are linked to the selected locus. 
The ancestral sex-determining locus is located at -0.05 and the novel sex-determining locus is located at 0.05, such that the probability of a cross-over between them is $\approx0.1$.
The x-axis gives the position of the locus under haploid selection.
We used Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
Parameters as in Figure \ref{fig:WinvasionLowR}.
}
\label{fig:InvasionVsCentiMorgans}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%W invasion versus position of selected locus
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
%\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgans}
\includegraphics[width=0.5\linewidth]{InvasionVsCentiMorgansAllOrders}
\caption{
Haploid selection allows a neo-$W$ to invade an ancestral $XY$ system regardless of how tightly it and the ancestral sex-determining locus are linked to the selected locus. 
The ancestral sex-determining locus is located at -0.05 and the novel sex-determining locus is located at 0.05 (corresponding to the peaks of invasion fitness), such that the probability of a cross-over between them is $\approx0.1$.
The x-axis gives the position of the locus under haploid selection.
We used Haldane's map function \citep[Equation 3 in ][]{Haldane1919} to convert from map distance (centiMorgans) to the probability of a cross-over event. 
Parameters as in Figure \ref{fig:WinvasionLowR}.
}
\label{fig:InvasionVsCentiMorgans}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
